Introducing Distributed Dynamic Data-intensive (D3) Science: Understanding Applications and Infrastructure

### 2016-08-17 3dpas_intro.tex
ongoing refinement.

In addition to the aforementioned hierarchy and granularity to which the term
application has been applied, the class of applications in any level differ
widely in scale, sophistication and type as well different objective and
objects.  Thus, it is inevitable that the non-contextual use of the word
application be a recipe for befuddlement.

@@

Another group of applications are {\em infrastructural applications}.
Applications of this type are collaborative, in that they depend on a context
that is often agreed upon by a community, most often in terms of how data is
stored by the community and how it is accessed, as well as, more often than not,
a weak consensus on the infrastructure to be
used. %\jhanote{Dan: Please confirm you are OK with this modified
%  defintion of infrastructural application}
This allows different
sub-applications (that we again refer to as `applications') to focus
on different stages, such as generating data, or processing data.
Answering a science question now may involve a set of applications
that need to be run in series, perhaps in different stages, that may
be run by different groups that do not frequently interact.  This type
of application includes: ATLAS/WLCG (a toroidal large hadron collider apparatus/worldwide large hadron collider computing grid, \S\ref{WLCGSteve}), LSST
(large synoptic survey telescope, \S\ref{astroAdam}), SOA (service-oriented architecture) Astronomy (\S\ref{astroSOAAdam}), Sensor
Network Application (\S\ref{sensorSimon}), Climate
(\S\ref{climateDan}), Interactive Exploration of Environmental Data
(\S\ref{envJon}), and Power Grids (\S\ref{power}).

>>>>

In addition to the aforementioned hierarchy and granularity to which the term
application has been applied, the class of applications in any level differ
widely in scale, sophistication and type as well different objective and
objects.  Thus, we warn the reader of the inevitable befuddlement that the
casual and non-contextual use of the word application can cause.

@@

Another group of applications are {\em infrastructural applications}.
Applications of this type are collaborative, in that they depend on a context
that is often agreed upon by a community, most often in terms of how data is
stored by the community and how it is accessed, as well as, more often than not,
a weak consensus on the infrastructure to be used.  This allows different
sub-applications (that we again refer to as `applications') to focus on
different stages, such as generating data, or processing data.  Answering a
science question now may involve a set of applications that need to be run in
series, perhaps in different stages, that may be run by different groups that do
not frequently interact.  This type of application includes: ATLAS/WLCG (a
toroidal large hadron collider apparatus/worldwide large hadron collider
computing grid, \S\ref{WLCGSteve}), LSST (large synoptic survey telescope,
\S\ref{astroAdam}), SOA (service-oriented architecture) Astronomy
(\S\ref{astroSOAAdam}), Sensor Network Application (\S\ref{sensorSimon}),
Climate (\S\ref{climateDan}), Interactive Exploration of Environmental Data
(\S\ref{envJon}), and Power Grids (\S\ref{power}).
